Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-12-08 Ben_Manuscripts/structure_paper/Draft.tex
updates

  The $z$-direction correlation functions show that layers in our model prefer
  to stack further apart than the 3.7 \angstrom~ suggested by experiment. We attempted equilibration
  with layers stacked 5.0 nm apart and to our surprise, we observed
  long-term stability of a qualitatively different configuration suggesting
  that we have found more than one metastable free energy basin, corroborating \ref{point:metastable}.
  %that the initial distance between layers can influence the approach towards 
  %equilibrium.
  \begin{itemize}
        \item Equilibrated systems built according to the 3.7 \angstrom~layer spacing
        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore
        structure.
        \item We will refer to this large set of configurations, with an open pore, as
        the ordered pore basin open pore (Figure~\ref{fig:OPbasin}).
        \item Simulations of systems built with layers stacked 5
        \angstrom~ apart results in a pore structure characterized by high radial
        disorder, while still maintaining partitioning between hydrophobic and
        hydrophilic regions.
 %MRS3: need to address the similar RDFs.  What data can show they are different? Or maybe they HAVE rdfs, but not good layering? Have you done the fourier transform on them? We can still rule them out based on the XRD, of course.  But surprising the same RDFs.
        \item This will be called the disordered pore basin (Figure~\ref{fig:DPbasin}).
        \item This LLC membrane may exist in at least two metastable states.
        \item The distinct difference in pore structure exhibited by each phase will
        likely lead to different transport mechanisms.
        \item Because the pore structure will vary between each basin, understanding
        which phase exists experimentally is necessary in order to ensure we are
        studying the system which actually dominates.
  \end{itemize}

@@

  % BJC: I'm not sure what to make of this figure right now. The parallel-displaced configuration shares
  % more with the disordered pore phase
  % MRS3: yeah, see my notes on this.  wE need to understand how it can be visually open, and still have this structure.  
  % doesn't this structur have a different pore-to-pore distance.
  \begin{figure}
  \centering
  \begin{subfigure}{0.55\textwidth}
        \includegraphics[width=1\linewidth]{offset_density.png}
        \caption{}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.55\textwidth}
        \includegraphics[width=1\linewidth]{layered_density.png}
        \caption{}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.55\textwidth}
        \includegraphics[width=1\linewidth]{disordered_density.png}
        \caption{}
        \label{fig:offset_density}
  \end{subfigure}
  \caption{(a) Parallel Displaced (b) Sandwiched (c) ``Disordered''}~\label{fig:densities}
  \end{figure}

%MRS3: this needs a caption, and need to write some text analyzing it.  The thing that throws me off is that the RDF's look about the same for parallel displaced and disordered!  That's pretty hard to rationalize with the idea that the pores are open vs. closed. What am I missing? Very interesting regardless!

>>>>

  The $z$-direction correlation functions show that layers in our model prefer
  to stack further apart than 3.7 \angstrom as suggested by experiment. We
  attempted equilibration with layers stacked 5.0 nm apart and to our surprise,
  we observed long-term stability of a qualitatively different configuration
  suggesting that we have found more than one metastable free energy basin,
  corroborating \ref{point:metastable}.
  \begin{itemize}
 	\item The diffraction pattern is different in the tail region
	\item The layer spacing is further apart
  \end{itemize}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.55\textwidth}
        \includegraphics[width=1\linewidth]{offset_density.png}
        \caption{}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.55\textwidth}
        \includegraphics[width=1\linewidth]{layered_density.png}
        \caption{}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.55\textwidth}
        \includegraphics[width=1\linewidth]{disordered_density.png}
        \caption{}
        \label{fig:offset_density}
  \end{subfigure}
  \caption{(a) Parallel Displaced (b) Sandwiched (c) ``Disordered''}~\label{fig:densities}
  \end{figure}
